Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-06-07 tese/intro.tex
possible end of SotA 1
[ADD] added first beamer presentation

	As \cite{geddes} states, \say{No computer in our lifetimes will ever rival a human voice’s capacity to conveying rich and complex social and emotional meaning} , although nothing replace the physical contact with a person while we communicate, we are at a time when we can do more than just a visual and verbal communication, hypermedia can be added to video and voice in order to extend its value. The concept of structured voice and video synchronized with hypermedia is called hypervoice.
        %RP a citação do geddes faz sentido? Parece estar a falar de voz gerada por computador e não de video conferencia onde o que ouvimos são outras pessoas!

@@

As \cite{geddes} said, the quality of the interaction worsens as the number of users increase. In our testing phase we will quantify and qualify the impact of increasing users on the interface and performance of our prototype.

>>>>

	As Martin Geddes states\cite{geddes}, \say{No computer in our lifetimes will ever rival a human voice’s capacity to conveying rich and complex social and emotional meaning} , although nothing replace the physical contact with a person while we communicate, we are at a time when we can do more than just a visual and verbal communication, hypermedia can be added to video and voice in order to extend its value. The concept of structured voice and video synchronized with hypermedia is called hypervoice.
        %RP a citação do geddes faz sentido? Parece estar a falar de voz gerada por computador e não de video conferencia onde o que ouvimos são outras pessoas!

@@

According to Martin Geddes, the quality of the interaction worsens as the number of users increase\cite{geddes}. In our testing phases we will quantify and qualify the impact of increasing users on the interface and performance of our prototype.

### 2015-06-07 tese/project.tex
[ADD] added first beamer presentation

WebRTC technology allows real-time communications between web browsers without the need to install and use additional applications or plug-ins. The nature of web browser applications already follow the hypermedia concept, which makes WebRTC the ideal technology to apply the hyper-linked communications concepts.
The native support of WebRTC in operating systems extends its usage to outside the web browser, allowing to explore functionalities that browsers are poor to support such as video recording and massive information storage.

Our goal in this project is to develop an application that leverages the Hyper-linked communications concept to enable colaborative real-time audio and video communication, enriched with other media types, that can be accessed live or accessed latter.
This application will target the web browser platform, resorting to WebRTC.

In this document, we present the current State Of The Art in hyper-linked communications and related technologies, propose an architecture to implemente an hyper-linked communication application based on WebRTC and provide a plan for its implementation and evaluation.

@@

\section{Conclusions}\label{concl} % English
The development of WebRTC by the World Wide Web Consortium (W3C) allows web browser-to-browser audio, video and data communication. WebRTC is enabling new usage scenarios for communication and collaboration applications. This and other technologies allow the Hyper-link concept to be applied to a new media: real-time audio and video.

  This project proposes a solution that uses WebRTC for creating an application that provides audio, data, text and data real-time communications. Theses communications will be enriched using hypermedia concepts, the possibility to record and playback its content and the integration of collaborative tools.

>>>>

\ac{WebRTC} technology allows real-time communications between web browsers without the need to install and use additional applications or plug-ins. The nature of web browser applications already follow the hypermedia concept, which makes \ac{WebRTC} the ideal technology to apply the hyper-linked communications concepts.
The native support of \ac{WebRTC} in operating systems extends its usage to outside the web browser, allowing to explore functionalities that browsers are poor to support such as video recording and massive information storage.

Our goal in this project is to develop an application that leverages the Hyper-linked communications concept to enable collaborative real-time audio and video communication, enriched with other media types, that can be accessed live or accessed latter.
This application will target the web browser platform, resorting to \ac{WebRTC}.

In this document, we present the current State Of The Art in hyper-linked communications and related technologies, propose an architecture to implement an hyper-linked communication application based on \ac{WebRTC} and provide a plan for its implementation and evaluation.

@@

\section{Conclusions}\label{concl} % English
The development of \ac{WebRTC} by the World Wide Web Consortium (W3C) allows web browser-to-browser audio, video and data communication. \ac{WebRTC} is enabling new usage scenarios for communication and collaboration applications. This and other technologies allow the Hyper-link concept to be applied to a new media: real-time audio and video.

  This project proposes a solution that uses \ac{WebRTC} for creating an application that provides audio, data, text and data real-time communications. Theses communications will be enriched using hypermedia concepts, the possibility to record and playback its content and the integration of collaborative tools.

### 2015-06-07 tese/schd01.tex
need conclusions and abstract
[ADD] modules, changed titles
Reviewed methodology
[ADD] added first beamer presentation

\tikzset{every picture/.style={xscale=0.51,yscale=0.51,transform shape}}

\begin{ganttchart}[vgrid, hgrid]{1}{36}
\gantttitle{2015}{28}
\gantttitle{2016}{8} \\
\gantttitle{Jun}{4}
\gantttitle{Jul}{4}
\gantttitle{Aug}{4}
\gantttitle{Sep}{4}
\gantttitle{Oct}{4}
\gantttitle{Nov}{4}
\gantttitle{Dec}{4}
\gantttitle{Jan}{4}
\gantttitle{Feb}{4} \\
\gantttitlelist{1,...,36}{1}\\
%First Group
\ganttgroup{Thesis}{1}{10} \\
\ganttbar{Task 1}{2}{3} \\
\ganttbar{Task 2}{4}{10} \\
\ganttbar{Task 3}{9}{12}\\
%\ganttlink{elem0}{elem1}
\ganttgroup{Resume}{1}{10} \\

%\ganttmilestone{Milestone 1}{11}
%Second Group
\ganttgroup{Implementation}{1}{1}\ganttgroup{}{4}{8}\ganttgroup{}{11}{26}\ganttgroup{}{29}{30} \\
\ganttbar{ICE configuration}{1}{1} \\
\ganttbar{XMPP configuration}{1}{1} \\
%\ganttlink{elem4}{elem5}
%\ganttmilestone{Milestone 1}{11}
%Third Group
\ganttbar{WebRTC basics}{4}{4} \\
\ganttbar{Video \& Audio Communication}{4}{5} \\
\ganttbar{Non-Interactive Record \& Playback}{6}{8} \\
\ganttbar{Interactive Record \& Playback}{11}{14}\\
\ganttmilestone{First Prototype}{18}\\
\ganttbar{Collaborative Environment}{15}{18}\\
\ganttmilestone{Second Prototype}{22} \\
\ganttbar{Interface Improvement I}{19}{22} \\
\ganttbar{Usability Tests I}{23}{23} \\
\ganttmilestone{Third Prototype}{25} \\
\ganttbar{Interface Improvement II}{24}{25} \\
\ganttbar{Usability Tests II}{26}{26} \\
\ganttbar{Performance Tests}{29}{30} \\
\ganttbar{Performance Improvements}{30}{30} \\
\ganttmilestone{Final Prototype}{30}

@@

\ganttlink{elem1}{elem2}
\ganttlink{elem2}{elem3}
\ganttlink{elem9}{elem11}
\ganttlink{elem10}{elem11}
\ganttlink[link type=F-S]{elem12}{elem13}
\ganttlink{elem13}{elem14}
\ganttlink[link type=F-S]{elem14}{elem16}
\ganttlink[link type=F-S]{elem16}{elem18}
\ganttlink[link type=F-S]{elem18}{elem19}
\ganttlink[link type=F-S]{elem19}{elem21}
\ganttlink[link type=F-S]{elem21}{elem22}
\end{ganttchart}

>>>>

The most important task in order to implement our project is the infrastructure, without it our project wouldn't work. The basic infrastructure will be our first concern, namely the Web Server configuration, ICE and signaling servers.

The Web development can only start after the basic infrastructure configuration. When leading with streams, the infrastructure will be complemented with stream servers.

There will be four prototypes, the first one should implement most of streaming and collaborative functionalities. The second prototype will have the same functionalities but a more friendly user interface which will be tested and reviewed by potential users. The third prototype will be an improvement based on the users feedback. In the final prototype we will improve our system performance.

\tikzset{every picture/.style={xscale=0.49,yscale=0.55,transform shape}}

\begin{ganttchart}[vgrid, hgrid]{1}{36}
\gantttitle{2015}{28}
\gantttitle{2016}{8} \\
\gantttitle{Jun}{4}
\gantttitle{Jul}{4}
\gantttitle{Aug}{4}
\gantttitle{Sep}{4}
\gantttitle{Oct}{4}
\gantttitle{Nov}{4}
\gantttitle{Dec}{4}
\gantttitle{Jan}{4}
\gantttitle{Feb}{4} \\
\gantttitlelist{1,...,36}{1}\\
%First Group
\ganttgroup{Thesis}{1}{35} \\
\ganttbar{Related work evaluation}{1}{30}\\
\ganttbar{Thesis writing}{19}{35} \\
\ganttbar{Paper writing}{25}{35} \\
\ganttmilestone{Delivery}{35}{35} \\
%\ganttlink{elem0}{elem1}
%\ganttgroup{Resume}{1}{10} \\

%\ganttmilestone{Milestone 1}{11}
%Second Group
\ganttgroup{Implementation}{1}{1}\ganttgroup{}{4}{8}\ganttgroup{}{11}{26}\ganttgroup{}{29}{30} \\
\ganttbar{Basic configuration}{1}{1} \\
%\ganttlink{elem4}{elem5}
%\ganttmilestone{Milestone 1}{11}
%Third Group
\ganttbar{WebRTC basics}{4}{4} \\
\ganttbar{Video \& Audio Communication}{4}{5} \\
\ganttbar{Non-Interactive Record \& Playback}{6}{8} \\
\ganttbar{Interactive Record \& Playback}{11}{14}\\
\ganttmilestone{First Prototype}{18}\\
\ganttbar{Collaborative Environment}{15}{18}\\
\ganttmilestone{Second Prototype}{22} \\
\ganttbar{Interface Improvement I}{19}{22} \\
\ganttbar{Usability Tests I}{23}{23} \\
\ganttmilestone{Third Prototype}{25} \\
\ganttbar{Interface Improvement II}{24}{25} \\
\ganttbar{Usability Tests II}{26}{26} \\
\ganttbar{Performance Tests}{29}{30} \\
\ganttbar{Performance Improvements}{30}{30} \\
\ganttmilestone{Final Prototype}{30}

@@

\ganttlink{elem9}{elem10}
\ganttlink[link type=F-S]{elem11}{elem12}
\ganttlink{elem12}{elem13}
\ganttlink[link type=F-S]{elem13}{elem15}
\ganttlink[link type=F-S]{elem15}{elem17}
\ganttlink[link type=F-S]{elem17}{elem18}
\ganttlink[link type=F-S]{elem18}{elem20}
\ganttlink[link type=F-S]{elem20}{elem21}
\end{ganttchart}

%RP o que estás duas semanas a fazer no final? Porque não entregas após a escrita. Se é tempo para eu rever, então deveria haver outra fase para corrigires. Penso que podemos considerar que isso fica tudo dentro do ``writting''. Se quiseres aumenta.

%RP troca ``essay writting'' por ``thesis writting''

### 2015-06-07 tese/state02.tex
[ADD] added first beamer presentation

  \ac{SIP} is used in \ac{VoIP} applications due to its compatibility with the \ac{PSTN}.
  Service providers are making their \ac{SIP} infrastructures available through WebSockets.
%RP a frase anterior é estranha
  Frameworks like \emph{jsSIP}\footnote{\url{http://jssip.net/}(accessed June 1, 2015).}, \emph{QoffeeSIP}\footnote{\url{http://qoffeesip.quobis.com/}(accessed June 1, 2015).} and \emph{sipML5}\footnote{\url{http://sipml5.org/}} are used on the client side to parse and encode \ac{SIP} messages, making \ac{SIP} accessible to web based applications. 
%RP quando usas footnotes para indicar sites deves acrescentar ``last accessed (data)''. Isto é importante pois os sites são documentos efémeros que podem dizer uma coisa diferente mais tarde.
  \ac{SIP} with \emph{WebSockets} can be used as a signaling method for \ac{WebRTC} applications, it allows web browsers to have audio, video and \ac{SMS} capabilities like mobile phones. For instance, it's possible to inter-operate web communications with \ac{SIP} networks, mobile and fixed phones.

>>>>

  \ac{SIP} is used in \ac{VoIP} applications due to its compatibility with the \ac{PSTN}.
  Service providers are making their \ac{SIP} infrastructures available through WebSockets.
%RP a frase anterior é estranha
  Frameworks like \emph{jsSIP}\footnote{\url{http://jssip.net/}(accessed June 1, 2015).}, \emph{QoffeeSIP}\footnote{\url{http://qoffeesip.quobis.com/}(accessed June 1, 2015).} and \emph{sipML5}\footnote{\url{http://sipml5.org/}(accessed June 1, 2015).} are used on the client side to parse and encode \ac{SIP} messages, making \ac{SIP} accessible to web based applications. 
%RP quando usas footnotes para indicar sites deves acrescentar ``last accessed (data)''. Isto é importante pois os sites são documentos efémeros que podem dizer uma coisa diferente mais tarde.
  \ac{SIP} with \emph{WebSockets} can be used as a signaling method for \ac{WebRTC} applications, it allows web browsers to have audio, video and \ac{SMS} capabilities like mobile phones. For instance, it's possible to inter-operate web communications with \ac{SIP} networks, mobile and fixed phones.
